%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Ryo Suzuki} % Your name
% \address{\today} % Your secondary addess (optional)
% \address{123 Broadway \\ City, State 12345} % Your address
\address{ryo.suzuki@colorado.edu \\ +1 (650) 485-3567 \\ http://ryosuzuki.org } % Your phone number and email
\address{DLC 170, University of Colorado Boulder, Boulder CO 80302}

\begin{document}

\begin{rSection}{Education}

{\bf Ph.D student in Computer Science, University of Colorado Boulder} \hfill {\em August 2015 - Present} \\
Coursework: User-Centered Design, Computer Graphics, Computer Vision, NLP, etc

{\bf M.A in Economics, University of Tokyo} \hfill {\em March 2013} \\
Top 5\% in Machine Learning, Microeconomics, and Macroeconomics

{\bf B.Eng in Engineering, Tokyo Institute of Technology} \hfill {\em March 2011} \\ 
GPA: 3.9

\end{rSection}

%----------------------------------------------------------------------------------------


\begin{rSection}{Research Experience}

{\bf University of Colorado Boulder HCI Group} \hfill {\em August 2015 - Present} \\
Advisor: Tom Yeh and Mark D. Gross

{\bf UC Berkeley BiD Group} \hfill {\em May 2016 - August 2016} \\
Advisor: Bjoern Hartmann

{\bf Stanford University HCI Group} \hfill {\em May 2015 - August 2015} \\
Advisor: Michael S. Bernstein

{\bf University of Tokyo IIS-Lab} \hfill {\em September 2014 - May 2015} \\
Advisor: Koji Yatani

{\bf AIST Media Interaction Group} \hfill {\em January 2015 - March 2015} \\
Advisor: Jun Kato

\end{rSection}



\begin{rSection}{Publications}

% {\bf Ryo Suzuki}, Jun Kato, Koji Yatani, {\it "ClassCode: A Web-based Environment for Programming Education in Classrooms."} (VL/HCC'17 in submission)

% {\bf Ryo Suzuki}, Tom Yeh, Koji Yatani, Mark D. Gross, {\it "Autocomplete Textures for 3D Printing."} (CHI'17 under review)

Andrew Head, Elena Glassman, Gustavo Soares, {\bf Ryo Suzuki}, Lucas Figueredo, Loris D'Antoni, Bjoern Hartmann, {\it "Writing Reusable Code Feedback at Scale with Mixed-Initiative Program Synthesis."} L@S'17 (to appear)


Reudismam Rolim, Gustavo Soares, Loris D'Antoni, Oleksandr Polozov, Sumit Gulwani, Rohit Gheyi, {\bf Ryo Suzuki}, Bjoern Hartmann, {\it "Learning Syntactic Program Transformations from Examples."} ICSE'17 (to appear)

{\bf Ryo Suzuki}, Niloufar Salehi, Michelle S. Lam,
Juan C. Marroquin, Michael S. Bernstein,
{\it "Atelier: Repurposing Expert Crowdsourcing Tasks as Micro-internships."} Proceedings of the CHI Conference on Human Factors in Computing Systems. ACM, 2016. (CHI'16)

Stanford Crowd Research Collective (For the full author list, please see the publication), {\it "Daemo: A Self-Governed Crowdsourcing Marketplace".} Proceedings of the Annual ACM Symposium on User Interface Software and Technology. ACM, 2015. (UIST'15 Adjunct)

{\bf Ryo Suzuki}, {\it "Toward a Community Enhanced Programming Education"}, Proceedings of the CHI Conference on Human Factors in Computing Systems. ACM, 2015. (CHI'15 EA)

{\bf Ryo Suzuki}, {\it "Interactive and Collaborative Source Code Annotation".}, Proceedings of the International Conference on Software Engineering. IEEE, 2015. (ICSE'15 Adjunct)

{\bf Ryo Suzuki}, {\it "Network Thresholds and Multiple Equilibria in the Diffusion of Content-based Platforms."} Proceedings of the International Conference on Web and Internet Economics. Springer, 2014. (WINE'14)

% {\bf Ryo Suzuki}, {\it "Incentive Structure on Open Source Software Community: Case Study of GitHub."} Economics and Computer Science Workshop at the University of Tokyo, 2014

% {\bf Ryo Suzuki}, {\it "Diffusion Process and Take-off Conditions of the Online Platform."} Economics and Computer Science Workshop at the University of Tokyo, 2014
\end{rSection}


\begin{rSection}{Awards and Honors}

{\bf Nakajima Foundation Scholarship} \hfill {\em November 2014} \\
{\bf KAKENHI Grants-in-Aid for Scientific Research} \hfill {\em April 2013} \\
{\bf JSPS Research Fellow DC1} \hfill {\em April 2013} \\
{\bf JASSO Fellow (Total Exemption for Particularly Outstanding Students) } \hfill {\em March 2013} \\
{\bf Tohso Foundation Scholorship} \hfill {\em April 2010} \\

{\bf Business Model Competition Japan 2014 Microsoft Award} \hfill {\em February 2014} \\
{\bf Tech Crunch Disrupt Tokyo 2013 Finalist} \hfill {\em November 2013} \\
{\bf 1st Prize Winner of University of Tokyo Entrepreneur Dojo} \hfill {\em October 2012} \\
% {\bf Honer of MOVIDA School} \hfill {\em May 2012} \\
\end{rSection}


\begin{rSection}{Teaching Experience}

{\bf Teaching Assistant at University of Tokyo} \hfill {\em October 2012 - February 2013} \\
Microeconomic Policy (Graduate) for Prof. Dan Sasaki

{\bf Teaching Assistant at International Christian University} \hfill {\em October 2012 - February 2013} \\
Statistics (Undergraduate) for Prof. Takuya Kaneko

{\bf Teaching Assistant at University of Tokyo} \hfill {\em April 2012 - August 2012} \\
Mathematics II (Graduate) for Prof. Kazuya Kamiya

{\bf Teaching Assistant at Tokyo Institute of Technology} \hfill {\em October 2010 - February 2011} \\
Advanced Macroeconomics (Graduate) for Prof. Takumi Naito

\end{rSection}


\begin{rSection}{Work Experience}

{\bf CTO at Dada, Inc} \hfill {\em August 2012 - March 2014} \\
Development of Samenos (http://samenos.com), a platform for artists, creators, and designers.

{\bf Software Engineer at Howtelevision, Inc} \hfill {\em December 2011 - December 2012} \\
Development of iOS application for Gaishishukatsu.com (http://gaishishukatsu.com).

{\bf Data Analyst at Manavee} \hfill {\em January 2012 - March 2012} \\
Analysis of user data at Manvee (http://manavee.com), a MOOC for high school students in Japan.

\end{rSection}


\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{3ex}} l }
Programming Languages & JavaScript, C/C++, Python, Ruby, Objective-C \\
Development Framework & OpenGL, WebGL, OpenCV, Tensorflow, Node.js, iOS, Arduino \\
Tools & Git, Adobe Illustrator, Adobe After Effects, Solidworks
% Databases & MySQL, PostgreSQL, MongoDB, Redis, Memcached \\
% Protocols \& APIs & JSON, REST, XML  \\
\end{tabular}

\end{rSection}



\end{document}
